Edge effects and optimal field sizes in Alberta

### 2021-06-22 Manuscript/manuscript.Rmd
Tried out AR1 models
- Model fits, but runs into problems when running adreport() - takes an incredibly long time

- At each field, we fit an additive model of the effect of boundary distance on crop yield while accounting for within-field spatial variation and temporal variation in the combine yield monitor
  - Ground speed is known to be extremely important to yield monitor accuracy [@arslan2002], with low ground speed registering higher yields 
  - Crop yield can vary within a field due to soil conditions, moisture, seeding rates, herbicide application, and previous agricultural practices 
    <!-- - such as strip farming -->
  - While sensor calibration can reduce combine-level bias (such as a combine recording consistently higher/lower yields across fields), this does not address sensor drift that occurs over time  within fields
  - This may be caused by sensors accumulating debris during harvest (pers. comm. Trent Clark), leading to changes in accuracy and bias over time

>>>>

- At each field, we fit an additive model of the effect of boundary distance on crop yield while accounting for within-field spatial variation and temporal variation in the combine yield monitor
  - Crop yield can vary within a field due to soil conditions, moisture, seeding rates, herbicide application, and previous agricultural practices 
    <!-- - such as strip farming -->
  - Ground speed is extremely important to yield monitor accuracy [@arslan2002], with low ground speed registering higher yields 
  - While sensor calibration can reduce combine-level bias (such as a combine recording consistently higher/lower yields across fields), this does not address sensor drift that occurs over time  within fields
  - This may be caused by sensors accumulating debris during harvest (pers. comm. Trent Clark), leading to changes in accuracy and bias over time
